\chapter{Elements required for a successful revolution}
  \epigraph{Victorious warriors win first and then go to war, while defeated warriors go to war first and then seek to win.}{Sun Tzu}
	\section{Legitimacy}
    \epigraph{Socialism never took root in America because the poor see themselves not as an exploited proletariat but as temporarily embarrassed millionaires.}{John Steinbeck}
      \paragraph{Since the entire point of an anarchist revolution is to achieve full communism, naturally, the population must believe in the idea as a whole. Without it, the public would reject and shun those who try and liberate them. Therefore, the public as a whole must have a class consciousness. The difficulty of this will vary from place to place - for example, in the USA, a common slogan is "the poor see themselves not as an exploited proletariat, but as temporarily embarrassed millionaires". On the other hand, in rural Aboriginal Australian communities, they are used to being continually oppressed and harassed by the government, and are well aware of their situation. Thus, it is more likely that a successful anarchist revolution will take hold in rural Aboriginal communities, as opposed to major American cities.}
      \paragraph{Another factor which increases legitimacy is culture. A culture that is inherently classist, racist, sexist, homophobic, transphobic, ableist, etc, will see an anarchist revolution as an evil to stamp out. On the other hand, a culture that is inherently helping and fostering of camaraderie will see the revolution as a step forward.}
       
    \section{Organisation}
      \paragraph{Without organisation, anarchy quickly degenerates into chaos. Likewise, any attempt at installing anarchism will }
    \section{Post-revolution plan}
    \section{Logistics}
    \section{Matériel}
    \section{Training}
    \section{Opportunity}