  \chapter{Levels of struggle and conflict}
    \section{Personal: the ideological}
      In the battle for
    \section{Cultural}
      Cultural struggle is the level of imperialism and colonialism. It is at this level where entire civilisations do battle, reguardless of whatever nation-state currently claims to represent them. 
    \section{Social}
      The social level of conflict is where society makes internal changes in its 
    \section{Political}
      \paragraph{The political level of conflict is the level of nation-states bickering and quarrelling, trade disputes, and so on.}
    \section{Strategic}
      \paragraph{The strategic level of conflict is the level of oil refineries, nuclear weapons, and factories. It can be thought of as the level which capitalism operates in order to support the political level.}
    \section{Theatre}
      \paragraph{The theatre level of conflict is the level of field armies, fronts, and supply dumps.}
    \section{Operational}
      \paragraph{The operational level of conflict is from the corps level down to the company level. An example is a battalion of infantry trying to secure a garrisoned village.}
    \section{Tactical}
      \paragraph{The tactical level is the platoon level down to the fire-team level. An example is a a platoon of troops securing a building.}
    \section{Personal: the combatant}
      \paragraph{The combatant level is the individual soldier or civilian. An example is an ordinary infantryman.}
      \epigraph{Of all the passions that inspire a man in a battle, none, we have to admit, is so powerful and so constant as the longing for honour and renown.}{Carl von Clausewitz\\ \textit{On War}}