
\documentclass[11pt,fleqn]{memoir} % Default font size and left-justified equations

\usepackage[top=3cm,bottom=3cm,left=3.2cm,right=3.2cm,headsep=10pt,a4paper]{geometry} % Page margins

\usepackage{xcolor} % Required for specifying colors by name
\definecolor{ocre}{RGB}{52,177,201} % Define the orange color used for highlighting throughout the book

\author{Laura Sakurai}
\title{The important of doctrine in praxis for the anarchist and communist revolution}
% Font Settings
%\usepackage{avant} % Use the Avantgarde font for headings
%\usepackage{mathptmx} 

%\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage[utf8]{inputenc} % Required for including letters with accents
%\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{epigraph}
% Bibliography
\usepackage[style=alphabetic,sorting=nyt,sortcites=true,autopunct=true,babel=hyphen,hyperref=true,abbreviate=false,backref=true,backend=biber]{biblatex}
\addbibresource{bibliography.bib} % BibTeX bibliography file
\defbibheading{bibempty}{}
\usepackage{enumitem}

%\input{structure} % Insert the commands.tex file which contains the majority of the structure behind the template

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------


\maketitle


%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

%\chapterimage{11081241_828603353860317_4962848819839491087_n.jpg} % Table of contents heading image

\pagestyle{empty} % No headers

\tableofcontents % Print the table of contents itself

%\pagestyle{fancy} % Print headers again

\part{Fundamentals}
  \input{on-libertarian-communism-in-the-west.tex}
  
  \input{introduction-to-terms.tex}
      
  \input{what-is-oppression.tex}
  \input{levels-of-struggle-and-conflict.tex}
  \chapter{Synthesism versus Platformism versus Insurrectionism}
    
  \input{revolutionary-ego.tex}
 
  \input{elements-required-for-a-successful-revolution.tex}
  


\part{Revolutionary skills and knowledge}
  \input{on-the-need-for-constant-study.tex}
    
      
  \input{decision-making.tex}

  \chapter{Organisation}
	\section{Auftragstaktik: Mission-type tactics, autonomy, its its appeal to Anarchists}
    \section{The fallacy of Insurrectionary and Individualist Anarchism}

  \chapter{Momentum, Morale, Manoeuvre and Mass: Basic principles of Strategic Action}
    \epigraph{It is better to go on striking in the same direction than to move one's forces this way and that.}{Carl von Clausewitz\\ \textit{On War}}
    

  \input{analysis.tex}
        
        
  \input{planning.tex}

        
  \chapter{Orders and coordination: Making sure everyone knows what to do}
    \section{Clarity vs confusion: Why plan?}
    \section{Considerations for good plans}
      From US Army FM-5.0
      \begin{description}[style=nextline]
        \item[Contain critical facts and assumptions]
          The commander and staff evaluate all facts and assumptions. They retain for future reassessment only those facts and assumptions that directly affect an operation’s success or failure. Assumptions are stated in OPLANs, but not in OPORDs.
        \item[Authoritative expression]
          The plan or order reflects the commander’s intention and will. Therefore, its language is direct. It unmistakably states what the commander wants subordinate commands to do.
        \item[Positive expression]
          Instructions in plans and orders are stated in the affirmative: for example, ``The trains will remain in the assembly area;'' instead of, ``The trains will not accompany the unit.'' As an exception, some constraints are stated in the negative: for example, ``Do not cross Phase Line Blue before H+2.''
        \item[Avoid qualified directives]
          Do not use meaningless expressions, such as, ``as soon as possible (ASAP).'' Indecisive, vague, and ambiguous language leads to uncertainty and lack of confidence. For example, do not use ``try to retain;'' instead, say ``retain until.'' Avoid using unnecessary modifiers and redundant expressions, such as ``violently attack'' or ``delay while maintaining enemy contact.'' Use ``attack'' or ``delay.'' Army doctrine already requires attacking violently and maintaining enemy contact during delays.
        \item[Balance]
          Balance centralized and decentralized control. The commander determines the appropriate balance for a given operation based on mission, enemy, terrain and weather, troops and support available, time available, and civil considerations (METT-TC). During the chaos of battle, it is essential to decentralize decision authority to the lowest practical level. Over centralization slows action and inhibits initiative. However, decentralized control can cause loss of precision. The commander constantly balances competing risks while recognizing that loss of precision is usually preferable to inaction.
        \item[Simplicity]
          Reduce all elements to their simplest form. Eliminate elements not essential to understanding. Simple plans are easier to understand. 
        \item[Brevity]
          Be clear and concise. Include only necessary details. Use short words, sentences, and paragraphs. Do not include material covered in SOPs (standing operating procedures). Refer to those SOPs instead. 
        \item[Clarity]
          Everyone using the plan or order must readily understand it. Do not use jargon. Eliminate every opportunity for misunderstanding the commander’s exact, intended meaning. Use acronyms unless clarity is hindered. Keep the plan or order simple. Use only doctrinal terms and graphics.  
        \item[Completeness]
          Provide all information required for executing the plan or order. Use doctrinal control measures that are understandable, and allow subordinates to exercise initiative. Provide adequate control means (headquarters and communications). Clearly establish command and support relationships. Fix responsibility for all tasks. 
        \item[Coordination]
          Provide for direct contact among subordinates. Fit together all battlefield operating systems (BOS) for synchronized, decisive action. Identify and provide for mutual support requirements while minimizing the chance of fratricide. 
        \item[Flexibility]
          Leave room for adjustments to counter the unexpected. The best plan provides for the most flexibility. 
        \item[Timeliness]
          Send plans and orders to subordinates in adequate time to allow them to plan and prepare their own actions. In the interest of timeliness, accept less than optimum products only when time is short.
      \end{description}
    \section{Five paragraph formats}
    \section{When a command structure is needed}
  
  \chapter{Action: Implementing the Schwerpunkt}
  	\section{Deception}
    \epigraph{All warfare is based on deception. Hence, when we are able to attack, we must seem unable; when using our forces, we must appear inactive; when we are near, we must make the enemy believe we are far away; when far away, we must make him believe we are near.}{Sun Tzu\\ \textit{The Art of War}}
    
    
  \chapter{Post-mortems and operational research}
  
  
  \chapter{Security}
    \epigraph{In making tactical dispositions, the highest pitch you can attain is to conceal them.}{Sun Tzu}
  
\part{Strategies and tactics}
  \chapter{Education and skill sharing}
  
  
  \chapter{Subverting the tools of the enemy to work against them}
  
  
  \chapter{Agitation, Propaganda, and the raising of class consciousness}
	\section{Symbols}
    \section{Memes: The poetry of the proletariat}
      \paragraph{One of the major features of social media sites are memes. What are memes, exactly? The idea comes from biology - it is "an idea, behaviour, or style that spreads from person to person within a culture". Examples include fashion trends, viral videos, pop-culture references, and chain emails. One particularly pervasive example, which we shall focus on, are captioned images. Image macros (i.e. a picture with text overlaid on it) and cartoons or comics are two examples of this type of meme. These can spread like wildfire on social media - indeed, one could say that they are a core part of what sets social media apart from traditional media.}
    
  \chapter{Liberals: Conversion of and working with}
  ``most important personal-political lesson of the last 2 years:
yeah, people got mixed-as-hell consciousness. it can be frustrating as fuck (and even dangerous on an individual level, which is why we organize). but if your politics are centered around a profound hatred of the masses then just admit you are interested in a subculture and not liberation please
and have the humility to admit that to yourself and realize that the social capital you are getting the consolatory benefits of is predicated on the isolation that is deadly to folks who can't afford to have a subculture in place of liberation.
i will take any salt-of-the-earth-type everyday working human with their messy interactions, lack of hipness to the social justice lingo, and basic willingness to learn ANYDAY over academic peddlers of hopelessness and ppl who gain idol status off of a post-modernist hate of the working masses.
You know who they are: they love to self-glorify in the model of individual education and call-out culture but are terrified of how actual radical education spaces attached to actual class struggle work will decentralize their individual selves.
get this: you aren't going to analyze oppression out of existence. say it again. you aren't going to analyze oppression out of existence. once more. analysis doesn't make a revolution. the masses do.
"Critiquing people where they are at is important, but we aren't gonna create the culture we want just by editing the culture capitalism creates." -Boots Riley
if we aren't talking about winning this thing, then we're done talking.'' - jamie saunders
  
  \chapter{Proving the illegitimacy of hierarchies, governments, and the ruling classes to ourselves and to the masses}
  
  
  \input{callout-culture-and-self-criticism.tex}

  \chapter{The Struggle for the Lumpenproletariat to be revolutionaries}
  Activists need support. You know who don't get much support in society? The lumpen. That's why it's harder for them to spend energy on being activists.
  
  
  \chapter{Demands versus objectives}
    Demands give the impression that the bourgeoisie have something that we want, and we are trying to get it from them; whereas objectives implies we are taking what we want by ourselves.

  \chapter{Violence, resistance, and oppression}

  \chapter{Public relations and the image of Anarchism}
    \section{Graffiti}
    \section{Riots}


  \chapter{Violence, terrorism, and coercion: Immoral and counter-productive}


  \chapter{Solidarity, forgiveness, sectarianism, and working together}



\part{Other topics}




\subsection{References}\index{References}

Since I found so much good information about pretty much everything I wanted to know about, I will just create a remark and let you know where you can find more specific information about, just like below.

%\begin{remark}
%Only the rarest, dankest, and most illegal of memes will subvert the public consciousness
%\end{remark}

\part{Appendices}
\input{references/secretwork.tex}
\end{document}