  \chapter{On the need for constant study}
    \epigraph{Hungry man, reach for the book: it is a weapon.}{Bertolt Brecht}
    \epigraph{I'm very good at integral and differential calculus;\\
  I know the scientific names of beings animalculous:\\
  In short, in matters vegetable, animal, and mineral,\\
  I am the very model of a modern Major-General.}{Gilbert and Sullivan \\ \textit{The Pirates of Penzance}}
    \section{Operational research}
	  \paragraph{Operational research is the mathematical field of optimal decision making. It has a lot of overlap with game theory, control theory, and probability. Examples of problems addressed in operational research are optimal machine placement on factory floors, determining the best location to reinforce armour on military vehicles, and determining the optimal scheduling of logistic shipments.}
    \subsection{Management science}
    	\paragraph{Management science can be defined as operational research applied to personnel management settings.}
    \subsection{Game theory}
    	\paragraph{Game theory, and its offshoots such as drama theory and confrontation analysis, can be thought of as \textit{interactive} operational research, where there are multiple decision makers, each with their own (not necessarily conflicting) objectives. Examples include air traffic control routing, where the aim is the maximise the maximum distance between planes on the same air corridor; pursuit-and-evasion scenarios such as finding the best way for a missile to hit a certain target behaving in a certain way; and automated stock trading.}
    \section{Military theory}

    \section{Marketing}
      \subsection{Guerilla marketing}
    \section{Sociology}